---
title: "marxan"
author: "Anna Calle"
date: "10/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Installation

- Download the marxanui R package from http://marxan.net/downloadmui/
- Install the R package on your computer with a command like this:
  R CMD INSTALL marxanui_0.1.2.tar.gz
*Note: need to install package dependencies (below) before installing package
*Note: need to run command in the right folder for it to be successful
- For more information read marxan.io guide (http://marxan.net/downloads/Marxan_io_rev39_user_guide.pdf)

```{r}
# Install R package dependencies
install.packages("doMC") # This package wasn't listed as a dependecy on marxan's website but it is required
install.packages("doParallel")
install.packages("foreach")
install.packages("foreign")
install.packages("gplots")
install.packages("Hmisc")
install.packages("iptools")
install.packages("labdsv")
install.packages("leaflet")
install.packages("maptools")
install.packages("PBSmapping")
install.packages("png")
install.packages("rgdal")
install.packages("rgeos")
install.packages("rhandsontable")
install.packages("rjson")
install.packages("shiny")
install.packages("shinyBS")
install.packages("sp")
install.packages("sqldf")
install.packages("vegan")
install.packages("xtable")
```




```{r}
# Launching the user interfaces from R
library(marxanui)       # Load the R package

launch_app("import")   # Launch the import app to import your own data

launch_app("marxan")    # Launch the marxan app to run Marxan

launch_app("mxptest")   # Launch the parameter testing app to do BLM, SPF calibration, and target sensitivity testing

launch_app("manage")   # Launch the manage app to manage your datasets
```

Creating a zip file

Once you have a Marxan dataset, assemble all the required files to prepare them for upload. You need these files:
- The input.dat input parameter file,
- The input folder with all the input files,
- The planning unit layer shapefile files.
The planning unit shapefile must have a planning unit id field called either: PUID, PU_ID, puid, or pu_id.
Put all the files in a directory with the name you want for your Marxan database then zip up the directory. This zip file is your Marxan dataset.
