---
title: "suitability"
author: "Anna Calle"
date: "10/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Suitability 

- Depth: 25-100m
- Min sea surface temp: >22째C
- Max sea surface temp: <32째C
- Distance to shore: <25 nm
- *Current velocity made no difference

- Reefs
- Artificial reefs
- Wetlands
- MPAs
- *No take zones made no difference

Defining variables
```{r}
min_depth <- -25
max_depth <- -100
min_sst_value <- 22
max_sst_value <- 32
max_dist_shore <- 46300 #25 nautical miles converted to meters

```



Reclassifying depth to have 1s only if it's in between 25-100m, and 0s otherwise

```{r}
# Read in file
depth_mask <- raster(paste0(path,"/depth_mask.tif"))

# Reclassification matrix for depth layer
rcl_mat_depth <- c(-Inf, max_depth, 0,
                   max_depth, min_depth, 1,
                   min_depth, Inf, 0)

# Reclassify the depth layer
depth_binary <- reclassify(depth_mask,rcl= rcl_mat_depth)

# Plot reclassified layer
plot(depth_binary)

```

Reclassify min SST layer to have 1s only if it is above 22째C, and 0s otherwise
```{r}
# Read in file
min_sst_mask <- raster(paste0(path,"/min_sst_mask.tif"))

# Reclassification matrix for min SST
rcl_matrix_min <- c( -Inf, min_sst_value, 0,
                min_sst_value, Inf, 1)

# Reclassify min SST
sst_binary_min <- reclassify(min_sst_mask, rcl = rcl_matrix_min)

# Plot reclassified layer
plot(sst_binary_min)
```


Reclassify max SST layer to have 1s only if it is less than 32째C, and 0s otherwise
```{r}
# Read in file
max_sst_mask <- raster(paste0(path,"/max_sst_mask.tif"))

# Reclassification matrix for min SST
rcl_matrix_max <- c( -Inf, max_sst_value, 1,
                max_sst_value, Inf, 0)

# Reclassify min SST
sst_binary_max <- reclassify(max_sst_mask, rcl = rcl_matrix_max)

# Plot reclassified layer
plot(sst_binary_max)
```

Reclassify distance to shore layer to have 1s only if it is less than 25nm, and 0s otherwise
```{r}
# Read in file
dist_shore <- raster(paste0(path,"/dist_shore.tif"))

# Reclassify matrix for distance to shore layer
rcl_matrix_dist_shore <- c( -Inf, 0, 0,
                            0, max_dist_shore, 1,
                            max_dist_shore, Inf, 0)

# Reclassify distance to shore layer
dist_shore_binary <- reclassify(dist_shore, rcl = rcl_matrix_dist_shore)

# Plot reclassified layer
plot(dist_shore_binary)
```


MPAS
```{r}
# Read in file
mpas_binary <- raster(paste0(path,"/mpas_binary.tif"))

# Plot
plot(mpas_binary)

```

Artificial reefs
```{r}
# Read in file
reefs_artificial_binary <- raster(paste0(path,"/reefs_artificial_binary.tif"))

# Plot
plot(reefs_artificial_binary)

```

Reefs
```{r}
# Read in file
reefs_artificial_binary <- raster(paste0(path,"/reefs_artificial_binary.tif"))

# Plot
plot(reefs_binary)

```

Wetlands
```{r}
# Read in file
reefs_artificial_binary <- raster(paste0(path,"/reefs_artificial_binary.tif"))

# Plot
plot(wetlands_binary)

```

No-take zones
```{r}
# Read in file
no_take_binary <- raster(paste0(path,"/no_take_binary.tif"))

plot(no_take_binary)

```


Suitable areas (Multiplicative)
```{r}
# Overlay all layers
# Note: they all need to have the same extent and resolution
# Change extent distance to shore 

# Overlay
suitable <- overlay(sst_binary_min, sst_binary_max, depth_binary, mpas_binary, wetlands_binary, reefs_binary, reefs_artificial_binary, no_take_binary, dist_shore_binary, fun = function(a,b,c,d,e,f,g,h,i){a*b*c*d*e*f*g*h*i})

# Plot suitable areas
plot(suitable)
map('world', fill = T, add = T, col = 'gray')
# 224 suitable cells!
```

Suitable areas (Additive)
```{r}
# Overlay all layers
# Note: they all need to have the same extent and resolution
suitable_2 <- overlay(sst_binary_min, sst_binary_max, depth_binary, mpas_binary, wetlands_binary, reefs_binary, reefs_artificial_binary, no_take_binary, dist_shore_binary, fun = function(a,b,c,d,e,f,g,h,i){a+b+c+d+e+f+g+h+i})

# Plot suitable areas
plot(suitable_2)
map('world', fill = T, add = T, col = 'gray')

```


Save raster
```{r}
writeRaster(x = suitable, filename = paste0(path,"/suitable.tif"), overwrite = T)

# reproject to epsg: 5880 and save
suitable_reprojected <- projectRaster( suitable, crs = "+proj=aea +lat_1=-2 +lat_2=-22 +lat_0=-12 +lon_0=-54 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs")

writeRaster(x = suitable_reprojected, filename = paste0(path,"/suitable_epsg5880.tif"), overwrite = T)

```


Total suitable area calculation
```{r}
a <- area(suitable)
plot(a)
b <- (suitable * a)
plot(b)

sum(values(b), na.rm = T)
```

```{r}
# Sanity check --> check area of EEZ
eez_r <- rasterize(eez_BRA, r, field = 1, background = 0)

a_eez <- area(eez_r)
plot(a_eez)
b_eez <- (eez_r * a_eez)
plot(b_eez)

freq(b_eez)

sum(values(b_eez), na.rm = T)
```


